\sysfull

### 2018-04-12 paper/intro.tex
fix reference in the intro

A static task decomposition model assumes that each
single task can execute to completion.  If the hardware energy buffer provides
inadequate energy to execute each single task to completion, a program will not
terminate~\cite{cleancut}. To avoid non-termination under adversarial 
energy conditions, \sys uses a timer-based {\em partial task commit} mechanism.
Partial commit avoids non-termination by committing the intermediate state of a long-running
task that has repeatedly failed and restarted.  Partial commit violates
task atomicity, but preserves forward progress; if a programmer knows that
task atomicity is crucial to correctness, they can disable partial commit
instead risking non-termination.

@@

\begin{itemize}
\item The first {\em adaptive} task-based intermittent execution model that dynamically coalesces tasks to avoid unnecessary commit overhead. 
\item The first software memory virtualization mechanism for an intermittent system that \sys uses to preserve the atomicity of coalesced tasks.
\item A fall-back dynamic task splitting mechanism that preserves forward progress despite executing tasks that are too large for a device's energy supply.
\item A fully-realized prototype of \sys that runs on real energy-harvesting devices~\cite{wisp,capy}, to be released as open source after publication. 
\item An evaluation directly comparing \sys to a state of the art task-based intermittent programming and execution model from prior work~\cite{alpaca}, showing that on a suite of benchmarks from the literature and several new workloads, \sys often has higher performance and is more flexible to varied energy conditions. 
\end{itemize}

Section~\ref{sec:background} provides background on intermittent computing.
Section~\ref{sec:overview} provides an overview of \sys, while
Sections~\ref{sec:coalescing} and~\ref{sec:memory} describe \sys's coalescing
and virtualization mechanisms.Section~\ref{sec:discussion} discusses \sys
design issues.  Sections~\ref{sec:methodology} and~\ref{sec:eval} describe
\sys's methodology and evaluation.  Section~\ref{sec:related} puts \sys in the
context of related work and Section~\ref{sec:conc} concludes and discusses
future work.

>>>>

A static task decomposition model assumes that each
single task can execute to completion.  If the hardware energy buffer provides
inadequate energy to execute each single task to completion, a program will not
terminate~\cite{cleancut_2018}. To avoid non-termination under adversarial 
energy conditions, \sys uses a timer-based {\em partial task commit} mechanism.
Partial commit avoids non-termination by committing the intermediate state of a long-running
task that has repeatedly failed and restarted.  Partial commit violates
task atomicity, but preserves forward progress; if a programmer knows that
task atomicity is crucial to correctness, they can disable partial commit
instead risking non-termination.

@@

\begin{itemize}
\item The first {\em adaptive} task-based intermittent execution model that dynamically coalesces tasks to avoid unnecessary commit overhead. 
\item The first software memory virtualization mechanism for an intermittent system that \sys uses to preserve the atomicity of coalesced tasks.
\item A fall-back dynamic task splitting mechanism that preserves forward progress despite executing tasks that are too large for a device's energy supply.
\item A fully-realized prototype of \sys that runs on real energy-harvesting devices~\cite{wisp,capybara}, to be released as open source after publication. 
\item An evaluation directly comparing \sys to a state of the art task-based intermittent programming and execution model from prior work~\cite{alpaca}, showing that on a suite of benchmarks from the literature and several new workloads, \sys often has higher performance and is more flexible to varied energy conditions. 
\end{itemize}

Section~\ref{sec:background} provides background on intermittent computing.
Section~\ref{sec:overview} provides an overview of \sys, while
Sections~\ref{sec:coalescing} and~\ref{sec:memory} describe \sys's coalescing
and virtualization mechanisms. Section~\ref{sec:discussion} discusses \sys
design issues. Sections~\ref{sec:methodology} and~\ref{sec:eval} describe
\sys's methodology and evaluation. Section~\ref{sec:related} puts \sys in the
context of related work and Section~\ref{sec:conc} concludes and discusses
future work.
